Bioverse: Origins of Life

### 2024-07-13 src/tex/ms.tex
discuss contextual support for biosignature detections

\subsection{Survey simulations with Bioverse}

@@

\subsection{Contextual support for potential biosignature detections} % corresponds to ... which conclusion?
\todo[inline]{discuss how planetary context may impact credibility of tentative biosignature detections (e.g., if there is a good fit with a predicted OOL pattern; or the opposite: the planetary context does not fit well to any OOL scenarios)}
As we have shown in Section~\ref{sec:results}, the interplay of \gls{NUV} evolution and \gls{HZ} occupancy strongly favors late spectral types for abiogenesis via the cyanosulfidic scenario.
This strong predicted correlation between stellar spectral type and the occurrence of life can be used to falsify \gls{ool} scenarios.
The constraint of this context is particularly strong if a candidate biosignature is detected on a planet orbiting an earlier type star, i.e., where it is unexpected in the context of this \gls{ool} scenario.

@@

\subsubsection{Stellar flares}
Our assumptions on past UV flux neglect the contribution of stellar flares, which may be hypothesized as an alternative source of UV light~\citep{Ranjan2017}.
This concerns mainly ultracool dwarfs, due to their low quiescent emission and high pre-main sequence stellar activity~\citep{Buccino2007,West2008}.
Recent work indicates that the majority of stars show inadequate activity levels for a sufficient contribution through flares~\citep{Glazier2020,Ducrot2020,Guenther2020}.
The biosignature surveys we simulated here may test the hypothesis of sufficient UV radiation via stellar flares.

>>>>

\subsection{Survey simulations with Bioverse}\label{sec:results-bioverse}

@@

\subsection{Contextual support for potential biosignature detections} % corresponds to ... which conclusion?
\todo[inline]{discuss how planetary context may impact credibility of tentative biosignature detections (e.g., if there is a good fit with a predicted OOL pattern; or the opposite: the planetary context does not fit well to any OOL scenarios)}
The predicted interplay of \gls{NUV} flux and \gls{HZ} occupancy in enabling abiogenesis via the cyanosulfidic scenario could in principle be used to add or remove credibility from a tentative biosignature detection.
For example, with a strong believe that this scenario is the only viable one for the origins of life, a biosignature detection on a planet orbiting a strongly UV-radiating star may add credibility to the detection.
Conversely, a biosignature detection on a planet estimated to have received very little UV~radiation would increase the likelihood of a false positive detection.
On the other hand, should the detection in the latter case be confirmed, it could be used to falsify the UV~hypothesis.

Unfortunately, our simulations do not yield a clear criterion for the credibility of a biosignature detection based on spectral type of the host star, as both FGK and M~dwarf samples show similar maximum past \gls{NUV} flux distributions.
The abiogenesis rate in both samples show similar trends with the threshold \gls{NUV} flux, and the fraction of inhabited planets drops at similar threshold fluxes (see Section~\ref{sec:results-bioverse}).
A potentially inhabited planet's host star spectral type may thus not be a strong indicator for the credibility of a biosignature detection in the context of the UV~hypothesis.

@@
